\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{fontawesome5}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\CPP}{C\nolinebreak[4]\hspace{-.05em}\raisebox{.25ex}{\footnotesize\bf ++}}

% Contact Info
\name{Sanchit Dass}
\address{0123456789 \\ Bengaluru \\ \href{mailto:mail@example.com}{mail@example.com}
 \\ \faGithub\ \href{https://github.com/example}{github.com/example} \\
   \faLinkedin\ \href{https://linkedin.com/in/example}{linkedin.com/in/example}
}

\begin{document}

    % 1. Professional Summary
    % \begin{rSection}{Professional Summary}
    %     Full Stack Software Engineer with experience building LLM-driven platforms, AI tooling, and scalable web
    %     applications across startups and enterprise environments. Strong background in Python, JavaScript
    %     and React with proven delivery of production AI pipelines, data extraction platforms, and cross-platform
    %     applications.
    % \end{rSection}

    % 2. Work Experience
    \begin{rSection}{Work Experience}
        \textbf{Software Engineer Specialist} \hfill Jul 2025 --- Nov 2025 \\
        xAI \hfill \textit{Remote, India}
        \begin{itemize}
            \item Curated high-quality open-source datasets across JavaScript, Python, and C++ for training Grok coding models, improving model coverage and realism.
            \item Resolved 10+ critical model issues by analyzing failures, refining system prompts, and validating fixes across reasoning and non-reasoning model variants.
            \item Reviewed and debugged AI generated code for real user projects (open source libraries, small apps, 2D games), ensuring outputs met functional requirements and performance expectations.
        \end{itemize}
        
        \textbf{Founding Engineer} \hfill Jan 2025 --- Apr 2025 \\
        FetchFox \hfill \textit{Mountain View, USA}
        \begin{itemize}
            \item Developed and maintained the FetchFox web application using Next.js, delivering end-user features and improving overall product reliability.
            \item Built one-click integrations for Snowflake and Google Sheets, leveraging official APIs and OAuth flows to streamline data export for users.
            \item Implemented a Python based MCP server to support FetchFox’s backend workflows and automation use cases.
            \item Created a benchmarking dashboard using Python and Streamlit for custom web scraping tasks, comparing model performance across standardized challenges to surface strengths and failure modes.
        \end{itemize}

        \textbf{Full Stack Intern} \hfill Apr 2024 --- Dec 2024 \\
        ICPC Foundation \hfill \textit{Boston, USA}
        \begin{itemize}
            \item Led development of a social media platform for competitive programmers using Flutter, owning architecture and delivery across authentication, feeds, messaging, and notifications.
            \item Designed and implemented a role based real time notification system, enabling ICPC competition admins to broadcast live announcements during the ICPC 2024 World Finals.
        \end{itemize}

        \textbf{Software Engineer} \hfill Jul 2020 --- Jun 2022 \\
        National Instruments \hfill \textit{Bengaluru, India}
        \begin{itemize}
            \item Led architectural changes enabling side by side RFmx installations, ensuring backward compatibility across releases by redesigning installation and versioning workflows.
            \item Reduced CI build time by ~27\% by optimizing Jenkins pipelines, directly improving developer iteration speed.
            \item Developed and maintained production-grade C++ APIs for RFmx signal analysis software, contributing to 4 major product releases.
            \item Built an automated Python-based testing framework integrated into nightly builds, significantly improving bug detection, triage speed, and release confidence.
            \item Drove migration from legacy Perforce to Git (Azure DevOps), modernizing source control and build pipelines while minimizing disruption to active development.
        \end{itemize}

        \textbf{Software Engineer Intern} \hfill Jan 2020 --- Jun 2020 \\
        National Instruments \hfill \textit{Bengaluru, India}
        \begin{itemize}
            \item Delivered an end-to-end inventory management system that replaced manual bookkeeping and eliminated frequent scheduling conflicts, by designing a React + Django platform used by RF developers across the lab.
            \item Integrated 500+ RF lab instruments with a centralized backend, enabling live status and availability tracking by consuming REST APIs exposed by each device and persisting telemetry in MySQL.
        \end{itemize}
    \end{rSection} 

    % 3. Skills
    \begin{rSection}{Skills}
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Programming Languages & Python, JavaScript, \CPP \\
            Technologies & React, Node.js, Django, Large Language Models, Amazon Web Services, Docker, Flutter \\
        \end{tabular}\\
    \end{rSection}

    % 4. Education
    \begin{rSection}{Education}
        \textbf{MS, Computer Science}, Purdue University \hfill {Aug 2022 --- Dec 2023}\\
        % \begin{itemize}
        %     \item GPA (Only include if higher than 3.5 / 4.0), Class of Honors (Only include if good)
        %     \item Other school awards like Dean’s List, scholarships, community awards, etc.
        %     \item Relevant Coursework: Advanced Class A, Advanced Class B, Advanced Class C
        % \end{itemize}
        \textbf{BE, Computer Science}, BMS College of Engineering \hfill {Aug 2016 --- Sep 2020}
    \end{rSection}

    % 5. Projects
    % \begin{rSection}{Projects}

    % \textbf{Role}, {Project Name} (\href{https://myproject.com}{myproject.com}) \hfill {MMM YYYY --- MMM YYYY}
    % \begin{itemize}
    %     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
    %     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
    % \end{itemize}

    % \textbf{Role}, {Project Name} (\href{https://github.com/my-project}{github.com/my-project}) \hfill {MMM YYYY --- MMM YYYY}
    % \begin{itemize}
    %     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
    %     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
    % \end{itemize}

    % \end{rSection}

    % 6. Awards
    % \begin{rSection}{Awards}
    %     \begin{itemize}
    %         \item \textbf{MIT Women's Health AI Hackathon} --- Winners of Most Innovative Idea \hfill {May 2025}
    %     \end{itemize}
    % \end{rSection}
\end{document}
